Probability Distribution Checks

### 2017-04-26 Analysis.Rmd
Finalise data cleaning and run analysis on AUDPS only
Finalised data cleaning (again). Data are now in a tidy data frame for
ordinal analysis. AUDPS has been generated from the tiller incidence
data and analysed using MCMCglmm

All raw data graphs have been updated

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
                                    random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernable patterns.

>>>>

# Separate the TRT column into the two treatments for analysis
AUDPS <- separate(data = AUDPS, col = TRT, into = c("WMGT", "NRTE"))

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2015, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(AUDPS ~ WMGT * NRTE, 
                                    random = ~REP, 
                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2016, ]),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

@@

The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernible patterns.

### 2017-04-26 Probability_distribution_checks.Rmd
Finalise data cleaning and run analysis on AUDPS only
Finalised data cleaning (again). Data are now in a tidy data frame for
ordinal analysis. AUDPS has been generated from the tiller incidence
data and analysed using MCMCglmm

All raw data graphs have been updated

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked.

@@

```{r, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(DS2015$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2015$TShB_incidence, "norm")

f2 <- fitdist(DS2015$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2015$TShB_incidence, "exp")

@@

```{r, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(DS2016$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2016$TShB_incidence, "norm")

f2 <- fitdist(DS2016$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2016$TShB_incidence, "exp")

@@

To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines. On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution. A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit. In this case, for the 2015 data, the leaf data fit a lognormal distribution best or exponential, for all others a normal distribution appears to be fine. Because of the non-normal residuals of the 2015 leaf sheath blight data we'll look at using something that can handle these data like `MCMCglmm`.

>>>>

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked, however, the data both fit a normal distribution.

@@

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS15$AUDPS, "norm")

@@

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS156 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS156$AUDPS, "norm")
plot(f1)
car::qqp(AUDPS156$AUDPS, "norm")

@@

To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines. On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution. A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit. Here both sets of data fit a normal distribution.
